The Impact of Class Immutability on NCSS

### 2020-04-06 paper1/article.tex
more

\documentclass[a4paper,UKenglish,cleveref, autoref]{lipics-v2019}
\bibliographystyle{plainurl}
\title{The Impact of Class Immutability on NCSS}
\author{Yegor Bugayenko}
  {Huawei Technologies Co., Ltd.}
  {Russian Research Institute (RRI)}{Moscow, Russia}{yegor.bugayenko@huawei.com}
\authorrunning{Yegor Bugayenko}
\ccsdesc[100]{Software and its engineering~Object oriented languages}
\keywords{Object-Oriented Programming, Constructors, Cohesion}
\usepackage[utf8]{inputenc}
\usepackage[inline]{enumitem}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{pgfplots}
\usepackage{verbatimbox}
\usepackage{interval}
\usepackage{hyperref}
\usepackage{minted}
  \setminted{fontsize=\footnotesize}
  \setminted{breaklines}
  \usemintedstyle{bw}
\newcommand{\code}[1]{\texttt{#1}}
\newenvironment{nicetable}
  {\setlength{\parindent}{0em}\medskip\small}
  {\medskip}
\begin{document}
\maketitle

@@

A list of Java repositories were retrieved from GitHub via their
public API. The first 50 repositories were taken, which satisfied
the selection criteria:
\begin{enumerate*}[label={\arabic*)}]
\item more than 1000 stars,
\item more than 200 Kb of data,
\item not archived,
\item public.
\end{enumerate*}
The list included popular Java open source products, like
Spring Framework, RxJava, Google Guava, and others.

Files with \texttt{.java} extension were taken from all repositories.
There were 20,500 files found.

NCSS metric was calculated for each Java class.

Immutability was calculated for each Java class. A class was considered
immutable if it didn't have any attributes without \texttt{final} modified.

The Figure~\ref{fig:1} demonstrates the results obtained. The x-axis is
the value of NCSS. The y-axis is the share of immutable classes among
all classes with the given NCSS.

\begin{figure}[h]
  \input{../ncss.tex}
  \caption{Distribution of classes by NCSS}
  \label{fig:1}
\end{figure}

The tendency is visually obvious: larger classes are less often immutable.

>>>>

% \documentclass[a4paper,UKenglish,cleveref, autoref]{lipics-v2019}
\documentclass[12pt]{article}
\bibliographystyle{plainurl}
\title{The Impact of Class Immutability on NCSS}
\author{Yegor Bugayenko\\Huawei Technologies Co., Ltd.\\Russian Research Institute (RRI)\\Moscow, Russia\\yegor.bugayenko@huawei.com}{}{}
% \authorrunning{Yegor Bugayenko}
% \ccsdesc[100]{Software and its engineering~Object oriented languages}
% \keywords{Object-Oriented Programming, Immutability, NCSS}
\usepackage[utf8]{inputenc}
\usepackage[inline]{enumitem}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{pgfplots}
\usepackage{verbatimbox}
\usepackage{interval}
\usepackage{hyperref}
\usepackage{minted}
  \setminted{fontsize=\footnotesize}
  \setminted{breaklines}
  \usemintedstyle{bw}
\newcommand{\code}[1]{\texttt{#1}}
\newenvironment{nicetable}
  {\setlength{\parindent}{0em}\medskip\small}
  {\medskip}
\input{../total}
\begin{document}
\raggedbottom
\maketitle

@@

A list of Java repositories were retrieved from GitHub via their
public API. The first \totalrepos{} repositories were taken, which satisfied
the selection criteria:
\begin{enumerate*}[label={\arabic*)}]
\item more than 1000 stars,
\item more than 200 Kb of data,
\item not archived,
\item public.
\end{enumerate*}
The list included popular Java open source products, like
Spring Framework, RxJava, Google Guava, and others.

Files with \texttt{.java} extension were taken from all repositories.
There were \totaljavafiles{} files found. Classes without a single
non-\texttt{static} attribute were excluded (including interfaces and enums).

NCSS metric and immutability were calculated for each Java class.
A class was considered immutable if it didn't have any
attributes without \texttt{final} modified.

The Figure~\ref{fig:1} demonstrates the results obtained. The x-axis is
the value of NCSS. The y-axis is the share of immutable classes among
all classes with the given NCSS. The diameter of the plot on the graph
is related to the amount of classes found for the specific NCSS.

\begin{figure}[h]
  \input{../ncss.tex}
  \caption{Distribution of class immutability by NCSS}
  \label{fig:1}
\end{figure}

The tendency is visually obvious: larger classes are less often immutable. It
is also obvious that the majority of classes have NCSS values smaller than 100.
